\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage[T1]{fontenc}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{Tanzim Hossain Romel}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \href{mailto:tanzimho@ualberta.ca}{tanzimho@ualberta.ca} |
    \href{mailto:tanhromel@gmail.com}{tanhromel@gmail.com} |
    \href{https://tanzimhromel.com}{tanzimhromel.com}
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    LinkedIn: \href{https://www.linkedin.com/in/thromel/}{thromel} | 
    GitHub: \href{https://github.com/thromel}{thromel}
    | \href{https://scholar.google.com/citations?user=zHV4EU8AAAAJ}{Google Scholar}
    }
\end{center}
\vspace{-6mm}
\begin{center}
    \small{Uttara, Dhaka, Bangladesh}
\end{center}

\vspace{-3mm}
\begin{center}
    \small{\textit{Software engineer and researcher with 3+ years of backend and AI engineering experience, building reliable AI-agent, developer-tooling, and healthcare analytics systems.}}
\end{center}

\vspace{-4mm}

\section{\textbf{Research Interests}}
\vspace{1mm}
\small{
AI for Software Engineering (AI4SE), Software Engineering for AI (SE4AI), Trustworthy AI, LLM Agent Security, Empirical Software Engineering, Developer Tooling
}
\vspace{-2mm}

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{University of Alberta}{Edmonton, Canada}
{Incoming M.Sc. in Computing Science}{Sep 2026}
\resumeItemListStart
\item Incoming thesis-based M.Sc. student in the \href{https://u-a-goose.github.io}{U-A-Goose} research group, supervised by \href{https://apps.ualberta.ca/directory/person/zy25}{Dr. Zhou Yang}, with affiliation to \href{https://www.amii.ca/}{Amii (Alberta Machine Intelligence Institute)}.
\resumeItemListEnd

\resumeSubheading
{Bangladesh University of Engineering and Technology (BUET)}{Dhaka, Bangladesh}
{B.Sc. in Computer Science and Engineering}{Mar 2018 - May 2023}
\resumeItemListStart
\item Selected coursework: Machine Learning, Operating Systems, Computer Security, Fault-Tolerant Systems, and High-Performance Database Systems.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}


\section{\textbf{Research Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {University of Illinois Urbana-Champaign (UIUC)}
  {Remote Research Intern through \href{https://uiuc-srse.github.io/}{UIUC++ SRSE 2026}; Professor \href{https://tianyin.github.io/}{Tianyin Xu's lab}}
  {Jun 2026 - Aug 2026}
  {{}}
\resumeItemListStart
  \item Working on software and systems reliability research with emphasis on rigorous empirical evaluation and reproducible research artifacts.
  \item Preparing research prototypes, benchmark artifacts, and evaluation evidence for agentic software engineering and reliability tasks.
  \item Building SRE-style benchmark artifacts around fault injection, mitigation oracles, shortcut rejection, and lifecycle evidence for Kubernetes reliability scenarios.
\resumeItemListEnd

\vspace{0.5mm}\item
  \textbf{\href{https://arxiv.org/abs/2601.14163}{An Empirical Study on Remote Code Execution in Machine Learning Model Hosting Ecosystems}}
  \hfill \textit{\footnotesize{Jun 2025 - Oct 2025}}\\
  \footnotesize{\textit{Tools: Python, Bandit, CodeQL, Semgrep, YARA | Manuscript under review at ACM TOSEM; preprint: \href{https://arxiv.org/abs/2601.14163}{arXiv:2601.14163}}}
  \vspace{-2.4mm}
\resumeItemListStart
  \item Conducted a large-scale study of \textasciitilde45,000 ML model repositories across Hugging Face, ModelScope, OpenCSG, OpenMMLab, and PyTorch Hub.
  \item Detected unsafe deserialization, eval-injection, malware-signature, and platform-safety risks using Bandit, CodeQL, Semgrep, YARA, and CWE-based classification.
  \item Analyzed 600+ developer discussions to build a taxonomy of misconceptions around remote code execution, trust flags, and model-loading safety.
  \item Compared platform defenses such as warning systems, scanning, SafeTensors support, and \texttt{trust\_remote\_code} controls to connect repository-level findings with ecosystem-level mitigation gaps.
\resumeItemListEnd

\resumeProject
  {The Choice Can Be the Attack: Auditing Aligned Backdoors in LLM Agents}
  {Tools: Python, vLLM, PyTorch, pandas, NumPy}
  {Aug 2025 - Present}
  {}
\resumeItemListStart
  \item Studied a hidden backdoor risk where a trigger changes which valid option an LLM agent chooses while the final answer still appears correct.
  \item Built \textbf{SHIFT}, which reruns the same task with and without a known trigger, then checks whether the changed choice favors the attacker's target rather than normal reasons like price or rating.
  \item Instrumented structured choice tasks with valid-option sets, logged option features, and matched no-trigger/trigger endpoint runs so the audit does not require model weights, logits, or hidden states.
\resumeItemListEnd

\resumeProject
  {Multi-Agent Framework for Generating Relational DB Schema \& ERD}
  {Tools: Python, LangGraph, StateGraph, Z3 Solver, SQLAlchemy, Text2Schema}
  {Jul 2025 - Present}
  {{}}
\resumeItemListStart
  \item Extended SchemaAgent with Dr. Sukarna Barua (BUET) to turn natural-language requirements into relational schemas and ER diagrams.
  \item Built a LangGraph pipeline for entity extraction, relationship detection, normalization checks, Z3 validation, and targeted retry.
  \item Designed verification gates for entity/relation completeness, functional dependencies, normal-form compliance, key soundness, requirement coverage, and executable DDL repair.
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Selected Research Software and Systems Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
{\href{https://github.com/thromel/ctxhelm}{ctxhelm + \href{https://github.com/thromel/helmbench}{HelmBench}: Context Compiler and Source-Free Agent Evaluation}}
{Tools: Rust, MCP, CLI, Git, Hybrid Retrieval, Symbol Indexing, JSON Schema, Agent Tracing}
{May 2026 - Present}
{}
\resumeItemListStart
\item Built a local-first, read-only context compiler for coding agents, combining lexical search, symbol search, dependency expansion, related-test mapping, git co-change hints, semantic metadata, and memory signals.
\item Shipped ctxhelm releases with archive/Homebrew installation, checksum verification, doctor checks, MCP smoke tests, and source-free evaluation artifacts.
\item Built HelmBench as active evaluation infrastructure with trace schemas, privacy checks, evidence bundles, matrix runs, and quality gates that separate context-selection quality from downstream patch quality without exposing source, prompts, transcripts, or terminal logs.
\resumeItemListEnd

\resumeProject
{\href{https://github.com/thromel/Yet-Another-C-Compiler}{Yet Another C Compiler}}
{Tools: C++17, Flex, Bison, CMake, x86-64 Assembly, SSA/IR Optimization}
{Jun 2021 - Aug 2021; revised Oct 2024}
{}
\resumeItemListStart
\item Built a C compiler with lexer/parser, semantic analysis, x86-64 code generation, and a linear-scan register allocator.
\item Modernized the Flex/Bison prototype with modular IR passes and SSA optimizations including SCCP, GVN, LICM, and dead-code elimination.
\resumeItemListEnd

\resumeProject
{\href{https://github.com/thromel/CSE-472-Machine-Learning}{Bangla Handwritten Digit Recognition}}
{Tools: Python, NumPy, OpenCV, CNN from Scratch, NumtaDB}
{Jan 2023 - Feb 2023}
{}
\resumeItemListStart
\item Implemented a NumPy CNN from scratch to recognize handwritten Bangla digits from the NumtaDB dataset.
\item Built the preprocessing and training pipeline, reaching \textbf{95.9\% accuracy} and placing \textbf{2nd among 120 students}.
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-2mm}
\section{\textbf{Open Source Contributions}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {Selected Upstream Contributions}
  {Selected upstream contributions across SRE benchmarks, program analysis, .NET, web servers, agent systems, and compilers}
  {2025 - 2026}
  {\href{https://github.com/thromel?tab=pull_requests}{GitHub}}
\resumeItemListStart
  \item \textbf{\href{https://github.com/SREGym/SREGym}{SREGym}}: authored and hardened Kubernetes SRE benchmark work, including scheduler priority-preemption and Calico route-reflector label-drift scenarios with fault/oracle design, validation checks, and reviewer-facing evidence.
  \item \textbf{\href{https://github.com/tsantalis/RefactoringMiner/pulls?q=author\%3Athromel}{RefactoringMiner}}: merged local MCP tooling, WebDiff workflow support, merge-parent-aware commit diffs, assertion migration matching, and single-page PR viewed toggles for refactoring-analysis workflows.
  \item \textbf{\href{https://github.com/dotnet/efcore}{EF Core}}: merged targeted data-stack changes for runtime migration creation/application, \texttt{ON DELETE SET DEFAULT} support, and nullable complex-property reload handling.
  \item \textbf{\href{https://github.com/Kaliumhexacyanoferrat/GenHTTP}{GenHTTP}}: added automatic request-body decompression and binary-response support with focused framework behavior tests.
  \item \textbf{\href{https://github.com/langchain-ai/deepagents/pull/2396}{deepagents}}: merged a CLI fix that stops and clears \texttt{LoadingWidget} animation timers on stop and unmount, preventing interval leaks in long-running terminal sessions and adding regression coverage for both cleanup paths.
  \item \textbf{\href{https://github.com/microsoft/typescript-go/pull/3314}{TypeScript}}: merged an upstream-aligned declaration-emit alias-resolution fix that preserves imported type aliases for inferred exports across module boundaries in Microsoft's Go port of TypeScript.
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-2mm}
\section{\textbf{Professional Experience}}
\vspace{-0.4mm}
  \resumeSubHeadingListStart
  \resumeSubheading
      {{IQVIA}}{Dhaka, Bangladesh}
      {Software Development Engineer}{Jun 2023 - Jun 2026}
      \resumeItemListStart
        \item Built and maintained KPI Library microservices in C\#/.NET and EF Core on AWS for healthcare analytics workflows over patient-level datasets, including API, filtering, aggregation, and export paths used by global pharmaceutical clients.
        \item Refactored a complex healthcare-analytics filter path into reusable query components, reducing duplicated business rules and improving filtering performance by 70\% in the targeted workflow.
        \item Reworked selected high-latency analytics paths with PostgreSQL query planning, targeted indexing, materialized views, Redis caching, and MongoDB tuning, reducing complex query time by 60\% and API latency by 40\%.
        \item Designed Playwright-backed export regression tests with multi-layer hashing to compare generated artifacts deterministically, raising export-workflow coverage from 72\% to 95\% and catching content-level regressions.
        \item Added OpenTelemetry and Jaeger tracing around API, query, and cache paths, making latency and regression sources visible across distributed services.
        \item Built LangGraph/LangChain workflows with MCP, RAG, and \texttt{deepagents} to map analyst prompts into structured dashboard setup, modification, drill-down analysis, and validated export actions, reducing setup effort by 85\% in the targeted workflow.
        \item Optimized CI/CD build stages and parallel test execution, reducing deployment time by 35\%; led POC work, mentored junior developers, and received the IQVIA Impact Program Silver Award for essential feature delivery.
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-2mm}
\section{\textbf{Skills}}
\vspace{-0.4mm}
\small{
\textbf{Primary:} Python, C\#/.NET, Rust, TypeScript, Go, PostgreSQL, AWS, Docker, Kubernetes, LangGraph, MCP \\
\textbf{Research and agent tooling:} CodeQL, Semgrep, Bandit, YARA, Z3, RefactoringMiner, deepagents, vLLM, JSON Schema, source-free tracing \\
\textbf{Systems and ML tooling:} C++, Java, Flex, Bison, CMake, NS-3, NumPy, OpenCV, PyTorch, Linux namespaces \\
\textbf{Backend and production tooling:} EF Core, SQLAlchemy, REST APIs, Redis, MongoDB, SQL Server, DynamoDB, OpenTelemetry, Jaeger, Playwright
}
\vspace{-2mm}


\section{\textbf{Honors and Awards}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumePOR{\href{https://github.com/thromel/CSE-472-Machine-Learning}{2nd Place -- Bangla Handwritten Digits Recognition}}{: 95.9\% accuracy, BUET ML Lab contest}{2022}
\resumePOR{Dean's List Award}{: academic performance, BUET Level 2}{}
\resumePOR{National Science Olympiads}{: prize winner in Bangladesh Physics and Chemistry Olympiads}{2017}
\resumePOR{Talentpool HSC Scholarship}{: 15th in Rajshahi Board with 95.6\% marks}{2017}

\resumeSubHeadingListEnd

\vspace{-6mm}

\section{\textbf{References}}
\vspace{-0.4mm}
\small{References available upon request.}
\vspace{-4mm}

\end{document}
